\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[pdfborder={0 0 0}]{hyperref}

\author{
    Lukas Prokop,
    Andi
}
\title{Digital library system in flask}
\date{\today}

\begin{document}
\maketitle
\tableofcontents

\section{Technology involved}
%
\begin{description}
  \item[Python]
    Our programming language in charge (version 2.7 is used).
  \item[Flask]
    Flask is a python micro-webframework written by Armin Ronacher.
    It features a very simple and basic API to provide web content easily
    and is extensible by plugins.
  \item[SQLAlchemy]
    SQLAlchemy is used as database binding (object relational mapped)
    to a postgresql database.
  \item[FlaskSQLAlchemy]
    SQLAlchemy binding for Flask.
  \item[PostgreSQL]
    We have decided in favor of postgresql as our database system.
  \item[Jinja2]
    This is our template engine (equivalently its template language).
  \item[Elastic search]
    Provides search capabilities to our dataset.
  \item[PDFMiner]
    A PDF parser capable of extracting the metadata.
\end{description}

\section{How to set it up}
%
\begin{enumerate}
  \item Run \texttt{virtualenv .} and \texttt{. bin/activate}
        as described at \href{http://flask.pocoo.org/docs/installation/#installation}%
        {Flask's installation page}.
  \item Run \texttt{pip install Flask} and \texttt{pip install elasticsearch}
        to install those packages for this repository locally.
  \item Run \texttt{python index.py} in the project's root directory to start the web application.
  \item Visit \url{http://localhost:5000/}.
\end{enumerate}

\section{Database layout}
%
We only use two tables. One table is called \emph{documents} which registers all documents. Attributes are:
\begin{description}
  \item[id] A basic integer primary key.
  \item[type] Which kind of document this is (e.g. ``doc'', ``attach'', ``comment'')
  \item[title] Title of the document
  \item[author] Who created this document?
  \item[timestamp] When was this document created?
  \item[parent] Which is the parent document?
\end{description}

Our second table stores various metadata, which attributes also its name \emph{metadata}.
\begin{description}
  \item[document] Which document is this metadata associated with?
  \item[key] An arbitrary key like \texttt{pdf.author} for the author in the metadata field of the PDF file.
  \item[value] The corresponding value for the given \texttt{key} of \texttt{document}.
\end{description}

\section{How to use it}
%
The requirements state that browsing, searching, inserting and presenting documents must be possible.
This corresponds to the following pages of the web application.
\begin{description}
  \item[Browsing]
    Documents can be browsed in the listing. You have to visit the list page.
  \item[Searching]
    Main (start) page. You can enter various search queries to retrieve documents from the dataset.
    The set of possible search queries is listed at the syntax page.
  \item[Inserting]
    The insertion can be done by visiting the upload page.
  \item[Presenting]
    Each document (and its associated documents) are presented on a separate page.
\end{description}

\section{Design decisions}
%
Technologically we have decided in favor of the Flask microframework,
because it allows easy setup of a small web application. It might not
be suitable for large web application with sophisticated user and content
management, but satisfies our needs for this assignment.

Concerning the database layout the requirement of a ``web-based institutional
repository for theses, papers, books'' can be reduced to managing the abstract
concept of ``documents''. So in general we do not distinguish between theses,
papers and books and only store them in one relation called ``documents''.

From the user perspective if the user wants to \emph{browse} documents,
we offer him a list of all available documents. These documents are associated
with their corresponding attachments by a parent-child relation. This way
the user gets an overview with the central element of a ``document''.

We decided to use the ElasticSearch storage engine to make search and retrieval
as easy as possible. It furthermore emphasizes a Service-Oriented Architecture
(SOA), because the search is maintained externally and data is retrieved by
a network socket and JSON.

Metadata like referenced articles in papers from PDFs cannot be extracted due
to missing semantical information in PDF. We focused on retrieving the Producer,
Creator (etc.) metadata fields which are part of the PDF standard. We use the
\texttt{pdfminer} python package for this task.

\texttt{pdfminer} is not supported in the python 3 branch and therefore we
used python 2.7 as our development and production system.

\end{document}
